\textbf{Socio-demographic determinants of COVID-19 vaccine uptake in Ontario: Exploring differences across the Health Region model}

### 2023-07-18 manuscript_v7/02-methods.qmd
updated

Because we identified differences between the percentage of participation within the socio-demographic factors of the survey considered in in our analysis and the percentage within these factors in the 2016 Census (such as participation within age groups and racial/ethnic groups), we used an iterative proportional fitting procedure (_raking_) [@deming1940] to correct the percentages within each socio-demographic variable using population totals obtained from the Census and OH; later, we fitted the regression model to the uncorrected and corrected data to determine if there were any differences in the obtanied estimates. Details regarding the correction can be found in the Appendix. All analyses were conducted in R 4.2.2 using the packages `survey` [@lumley2011],`tidyverse` [@wickham2019], `quarto` [@quarto], `modelsummary` [@modelsummary], and `gtsummary` [@gtsummary].

>>>>

Because we identified differences between the percentage of participation within each of the socio-demographic variables collected by the survey that were considered in our analysis and the percentage within these factors in the 2016 Census (such as participation by age and racial/ethnic groups), we used an iterative proportional fitting procedure (_raking_) [@deming1940] to correct the percentages within each socio-demographic variable using population totals obtained from the Census and OH; later, we fitted the regression model to the uncorrected and corrected data to determine if there were any differences in the obtanied estimates. Details regarding the correction can be found in the Appendix. All analyses were conducted in R 4.2.2 using the packages `survey` [@lumley2011],`tidyverse` [@wickham2019], `quarto` [@quarto], `modelsummary` [@modelsummary], and `gtsummary` [@gtsummary].

### 2023-07-18 manuscript_v7/main.tex
updated

\date{}
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

@@

Because we identified differences between the percentage of
participation within the socio-demographic factors of the survey
considered in in our analysis and the percentage within these factors in
the 2016 Census (such as participation within age groups and
racial/ethnic groups), we used an iterative proportional fitting
procedure
(\emph{raking})\textsuperscript{\protect\hyperlink{ref-deming1940}{50}}
to correct the percentages within each socio-demographic variable using
population totals obtained from the Census and OH; later, we fitted the
regression model to the uncorrected and corrected data to determine if
there were any differences in the obtanied estimates. Details regarding
the correction can be found in the Appendix. All analyses were conducted
in R 4.2.2 using the packages
\texttt{survey}\textsuperscript{\protect\hyperlink{ref-lumley2011}{51}},\texttt{tidyverse}\textsuperscript{\protect\hyperlink{ref-wickham2019}{52}},
\texttt{quarto}\textsuperscript{\protect\hyperlink{ref-quarto}{53}},
\texttt{modelsummary}\textsuperscript{\protect\hyperlink{ref-modelsummary}{54}},
and
\texttt{gtsummary}\textsuperscript{\protect\hyperlink{ref-gtsummary}{55}}.

>>>>

\date{}
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, interior hidden]}{\end{tcolorbox}}\fi

@@

Because we identified differences between the percentage of
participation within each of the socio-demographic variables collected
by the survey that were considered in our analysis and the percentage
within these factors in the 2016 Census (such as participation by age
and racial/ethnic groups), we used an iterative proportional fitting
procedure
(\emph{raking})\textsuperscript{\protect\hyperlink{ref-deming1940}{50}}
to correct the percentages within each socio-demographic variable using
population totals obtained from the Census and OH; later, we fitted the
regression model to the uncorrected and corrected data to determine if
there were any differences in the obtanied estimates. Details regarding
the correction can be found in the Appendix. All analyses were conducted
in R 4.2.2 using the packages
\texttt{survey}\textsuperscript{\protect\hyperlink{ref-lumley2011}{51}},\texttt{tidyverse}\textsuperscript{\protect\hyperlink{ref-wickham2019}{52}},
\texttt{quarto}\textsuperscript{\protect\hyperlink{ref-quarto}{53}},
\texttt{modelsummary}\textsuperscript{\protect\hyperlink{ref-modelsummary}{54}},
and
\texttt{gtsummary}\textsuperscript{\protect\hyperlink{ref-gtsummary}{55}}.
